---
weight: 11
title: "Job Repository"
author: "Lenny Lin"
date: 2023-02-06
categories: ["R"]
tags: []
output: 
  html_document:
    css: report_v05.css
    toc: true
    toc_float: true
    collapsed: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r, include=F}
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_lifelabs.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_consultant.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_aecl.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_swastika.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_northern_college.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_testmark.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_sgs.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_total.R")
```



# Experience

## LifeLabs

`r do.call(paste, c(lifelabs, sep = "", collapse = NULL))` 


## Consultant  

`r do.call(paste, c(consultant, sep = "", collapse = NULL))` 


## AECL  

`r do.call(paste, c(aecl, sep = "", collapse = NULL))` 


## Swastika  

`r do.call(paste, c(swas, sep = "", collapse = NULL))` 


## Testmark  

`r do.call(paste, c(testmark, sep = "", collapse = NULL))`


## Northern College  

`r do.call(paste, c(college, sep = "", collapse = NULL))`



## SGS  

`r do.call(paste, c(sgs, sep = "", collapse = NULL))`



## TOTAL  

`r do.call(paste, c(total, sep = "", collapse = NULL))`


# Training

## Leadership
AECL Leadership Academy and Toastmasters

Pinawa, MB

2009, 2010

## Data Scientist with R
DataCamp

Online

2019 *-* 2022



## Design of Experiments for Optimisation
udemy

Online

2022



## Design and Analysis of Experiments | DOE
udemy

Online

2022

# Recognition Award

*-*   Voyageur Certificate of Recognition Award for retaining lab accreditation to the ISO 17025 re-accreditation
