---
title: "Job Repository"
author: "Lenny Lin"
date: 2023-02-06
categories: ["R"]
tags: []
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r, include=F}
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_lifelabs.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_consultant.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_aecl.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_swastika.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_northern_college.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_testmark.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_sgs.R")
source("/Job Hunting/Job applications/applications after 2022.11.30/job duty repository/repository_total.R")
```



<br>
**LifeLabs**
<br>
`r do.call(paste, c(lifelabs, sep = "", collapse = NULL))` 

<br>
**Consultant**  
<br>
`r do.call(paste, c(consultant, sep = "", collapse = NULL))` 

<br>
**AECL**  
<br>
`r do.call(paste, c(aecl, sep = "", collapse = NULL))` 

<br>
**Swastika**  
<br>
`r do.call(paste, c(swas, sep = "", collapse = NULL))` 

<br>
**Testmark**  
<br>
`r do.call(paste, c(testmark, sep = "", collapse = NULL))`

<br>
**Northern College**  
<br>
`r do.call(paste, c(college, sep = "", collapse = NULL))`


<br>
**SGS**  
<br>
`r do.call(paste, c(sgs, sep = "", collapse = NULL))`


<br>
**TOTAL**  
<br>
`r do.call(paste, c(total, sep = "", collapse = NULL))`